X-ray phase-contrast imaging at 100 keV on a conventional source

### 2013-11-29 hedpc.tex
no siunitx

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
%\usepackage{pnastwof}

%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\DeclareSIUnit{\voltpeak}{Vp}

@@

\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    \SI{150}{\kilo\electronvolt} are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}

@@

Here we show a Talbot-Lau grating interferometer based on a novel optical
design, enabling imaging at X-ray energies of~\SI{100}{\kilo\eV} and above
with a large field of view as well as a very compact and efficient geometry.

@@

The vast majority of phase-sensitive techniques, including crystal analyzer
based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on polychromatic microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures~\cite{Munro2012} and Talbot-Lau
interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
recently extended to tube sources~\cite{Nesch2009,Parham2009}
but only at energies up
to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
In addition to phase sensitivity, analyzer-based and Talbot interferometry 
approaches also provide (with different retrieval mechanisms)
information about the integrated local small angle scattering power from
microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}. This signal is known under the name of dark-field, scatter or visibility reduction contrast.

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or CT require an acceleration voltage between \num{100} and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here we introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on
Talbot-Lau
interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
arrangement. 
Our solution removes one on the major hurdle which prevented grating interferometry to be applied at very high X-ray energies so far, namely the fabrication of gratings with high-aspect ratios.
 The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the fabrication process, usually
photolithography~\cite{David2002} or X-ray lithography~\cite{Mohr2012} as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The largest aspect ratios achieved by current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.

Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is only limited by the grating size to
$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with this
method and the available technology on larger wafers. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

\section{Results and discussion}
Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.

Edge-on illuminated grating interferometry finally allows phase contrast
imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on conventional X-ray
sources. With a circular distribution of the gratings, the diffracting and
absorbing structures can be matched to the divergent beam, even for very
compact geometries. Short, high-energy phase-contrast systems enable the
efficient investigation of high-density materials or thick samples,
adding information on electron density and integrated small angle scattering
power to the conventional absorption based signal. This will improve
material discrimination and density sensitivity capabilities in future
X-rays or even neutron~\cite{Grunzweig2008} investigations.

@@

%% Enter any subheads and the Materials and Methods text below.
\begin{materials}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is $\SI{80}{\micro \metre}$. The collimating slit right after the source is 
$\SI{25}{\micro \metre}$ large, while the second slit before the detector is
$\SI{100}{\micro\metre}$.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The SNR is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~\SI{14}{\percent} already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
\end{materials}

@@

\begin{figure}
    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

>>>>

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
\usepackage{upgreek}
\usepackage{xspace}
%\usepackage{pnastwof}

%% New commands
\newcommand{\micro}{\ensuremath{\upmu}}
\newcommand{\percent}{\%\xspace}
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}

@@

\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between 80 and
    150 keV are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    100 keV using a conventional X-ray tube and a
    compact geometry, with a total length of 54 cm. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}

@@

Here we show a Talbot-Lau grating interferometer based on a novel optical
design, enabling imaging at X-ray energies of~100 keV and above
with a large field of view as well as a very compact and efficient geometry.

@@

The vast majority of phase-sensitive techniques, including crystal analyzer
based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on polychromatic microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures~\cite{Munro2012} and Talbot-Lau
interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
recently extended to tube sources~\cite{Nesch2009,Parham2009}
but only at energies up
to the tungsten $K_\alpha$ line at~60 keV.
In addition to phase sensitivity, analyzer-based and Talbot interferometry 
approaches also provide (with different retrieval mechanisms)
information about the integrated local small angle scattering power from
microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}. This signal is known under the name of dark-field, scatter or visibility reduction contrast.

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
82 keV~\cite{Willner2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at 60 keV mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or CT require an acceleration voltage between 100 and
150 kVpeak. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here we introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on
Talbot-Lau
interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
arrangement. 
Our solution removes one on the major hurdle which prevented grating interferometry to be applied at very high X-ray energies so far, namely the fabrication of gratings with high-aspect ratios.
 The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the fabrication process, usually
photolithography~\cite{David2002} or X-ray lithography~\cite{Mohr2012} as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=25 keV$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=100 keV$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The largest aspect ratios achieved by current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= 2.8 \micro m$ for all gratings has been used. The design energy
is 100 keV and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = 19.8 \micro m$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
800 \micro m$
it can sufficiently attenuate X-rays up to energies of 
160 keV. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of 158 mm. The
source grating splits the relatively large focal spot ($\sim
1 mm$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = 800 \micro m$.

Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer (50 keV to
more than 160 keV) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
160 keV), the voltage of the X-ray source was set to
the maximum of 160 kV. With a grating structure height of
approximately 100 \micro m, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is only limited by the grating size to
30 mm, but wider gratings can be fabricated with this
method and the available technology on larger wafers. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

\section{Results and discussion}
Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
100 \micro m along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.

Edge-on illuminated grating interferometry finally allows phase contrast
imaging to be performed at high energies ($>100 keV$) on conventional X-ray
sources. With a circular distribution of the gratings, the diffracting and
absorbing structures can be matched to the divergent beam, even for very
compact geometries. Short, high-energy phase-contrast systems enable the
efficient investigation of high-density materials or thick samples,
adding information on electron density and integrated small angle scattering
power to the conventional absorption based signal. This will improve
material discrimination and density sensitivity capabilities in future
X-rays or even neutron~\cite{Grunzweig2008} investigations.

@@

%% Enter any subheads and the Materials and Methods text below.
\begin{materials}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times 60 mm^2$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at 100 keV
is a symmetric Talbot-Lau interferometer with a grating period of $p =
2.8 \micro m$ for all gratings. The distance from the source
grating to the analyzer grating is 32 cm and the source
grating is positioned 23 cm away from the source.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of 160 kV. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
1 mm. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of 600 \micro m
thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is 80 \micro m. The collimating slit right after the source is 
25 \micro m large, while the second slit before the detector is
100 \micro m.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (5 \percent). The exposure time was chosen in order to
get a low noise in the differential phase image. The SNR is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~14 \percent already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
\end{materials}

@@

\begin{figure}
    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        150 keV in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of 15 s per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}
